Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
figures

Additionally, eigenvectors associated with $\hat{\lambda}_1$ and
$\hat{\lambda}_2$ of the covariance matrix correspond to principal curvature
directions $\PrincDirH{1}{R}$ and $\PrincDirH{2}{R}$. The smallest eigenvector
corresponds to the normal direction $\NormalDirH{R}$ at $\vx$. Convergence
results can be found in \cite{ChapterIICurvature}.\todo{Changer
ChapterIICurvature dans le bibtex...}

@@

Representing a hierachical structure on GPU is usually challenging since the GPU
memory is limited and non consistent \todo{fix coherent/aligned/coalesced?}
memory access (\emph{e.g.} tree traversal using pointer dereferencing) may lead
to huge payload from cache misses.  Efficient spatial tree encoding can be
achieved using pointerless structures. We use linear quadtrees or octrees to
represent classical quadtree/octree trees, see for instance
\textsc{Gargantini}~\cite{gargantini1982effective}. This structure consists in
indexing each cell by a \emph{Morton code}: the code of children cells are
defined by the code of the parent suffixed by two bits (in dimension 2, three
bits in dimension 3) (see Figure \ref{fig_quadtree_partitionning}-\emph{left}).
A cell's code encodes its position \wrt its parent cell and its
complete path to the tree root. Hence, whatever their depth, all cell codes are
simply stored in a linear vector on memory. Furthermore, cell operations such as
subdivision, merging, neighbors access can be efficiently implemented using
bitwise operations on the Morton code. In the following, we use the GPU
implementation proposed by \textsc{Dupuy} \textit{et al.}~\cite{dupuy2014quadtrees}. By
using their approach, Morton codes and bitwise operations are optimized to match
with GPU hardware requirements.

@@

\todo[inline]{phrase sur approx si on met}

@@

@@

\begin{figure}
  \begin{center}
    \subfigure[]{\framebox{K}}
   \subfigure[]{\framebox{H}}
   \subfigure[]{\framebox{DIR1}}
   \subfigure[]{\framebox{DIR2}}
   \subfigure[]{\framebox{normales}}\\
    \subfigure[]{\framebox{K}}
   \subfigure[]{\framebox{H}}
   \subfigure[]{\framebox{DIR1}}
   \subfigure[]{\framebox{DIR2}}
   \subfigure[]{\framebox{normales}}

  \end{center}
  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.
    %
    For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
  \label{fig:full}
\end{figure}

>>>>

Additionally, eigenvectors associated with $\hat{\lambda}_1$ and
$\hat{\lambda}_2$ of the covariance matrix correspond to principal curvature
directions $\PrincDirH{1}{R}$ and $\PrincDirH{2}{R}$. The smallest eigenvector
corresponds to the normal direction $\NormalDirH{R}$ at $\vx$. Convergence
results can be found in \cite{CVIU2014}.%%% Changer avec le chapitre de Jaco à un moment

@@

Representing a hierachical structure on GPU is usually challenging since the GPU
memory is limited and non consistent %\todo{fix coherent/aligned/coalesced?}
memory access (\emph{e.g.} tree traversal using pointer dereferencing) may lead
to huge payload from cache misses.  Efficient spatial tree encoding can be
achieved using pointerless structures such as linear quadtrees or octrees, see
for instance \textsc{Gargantini}~\cite{gargantini1982effective}. This structure
consists in indexing each cell by a \emph{Morton code}: the code of children
cells are defined by the code of the parent suffixed by two bits (in dimension
2, three bits in dimension 3) (see Figure
\ref{fig_quadtree_partitionning}-\emph{left}). A cell's code encodes its
position \wrt its parent cell and its complete path to the tree root. Hence,
whatever their depth, all cell codes are simply stored in a linear vector on
memory. Furthermore, cell operations such as subdivision, merging, neighbors
access can be efficiently implemented using bitwise operations on the Morton
code. In the following, we use the GPU implementation proposed by \textsc{Dupuy}
\textit{et al.}~\cite{dupuy2014quadtrees}. By using their approach, Morton codes
and bitwise operations are optimized to match with GPU hardware requirements.

@@

%\todo[inline]{phrase sur approx si on met}

@@

For all illustrations, we use directly normal vectors computed by algorithm
discussed in Section~\ref{sec:curv-tens-estim}

@@

\begin{figure}
  \begin{center}
   \includegraphics[width=5cm]{figs/snow_I08iso_233_r20_l0_m3}

  \end{center}
  \caption{Illustration of mean curvature computation of snow microstructures.}
  \label{fig:full}
\end{figure}

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_mean}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_k1}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_k2}}\\
    {\includegraphics[width=2.7cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_dir_min_zoom}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_dir_max_zoom}}\\
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.
    %
    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}
